---
title: "R Notebook"
output: html_notebook
---
delete all 
```{r}
# Data loading
rm(list=ls())
```

# Load libraries
```{r}
library("ggplot2")
# install.packages("nortest")
library(nortest)
#install.packages("mvoutlier")
library(mvoutlier)
#install.packages("doBy")
library(doBy)
# install.packages("anytime")
library(anytime)
```

# Load rawdata set
```{r}
# load("../../../Data/rawdata_environment.RData")
```
# load from data set and save to r object
```{r}
# rawdata <- read.csv("../../../Data/training_set_VU_DM_2014.csv", header= TRUE)
# save.image("../../../Data/rawdata_environment.RData")

```
# make envorument file from rdata
```{r}
load(file = "../../../Data/data_Pclass1.RData")
load(file = "../../../Data/data_Pclass2.RData")
load(file = "../../../Data/data_Pclass3.RData")
load(file = "../../../Data/data_Pclass4.RData")
load(file = "../../../Data/data_Pclass5.RData")
load(file = "../../../Data/data_Pclass6.RData")

# load(file = "../../../Data/dataTEST_Pclass1.RData")
# load(file = "../../../Data/dataTEST_Pclass2.RData")
# load(file = "../../../Data/dataTEST_Pclass3.RData")
# load(file = "../../../Data/dataTEST_Pclass4.RData")
# load(file = "../../../Data/dataTEST_Pclass5.RData")
# load(file = "../../../Data/dataTEST_Pclass6.RData")


# save.image("../../../Data/rawdata_environment.RData")

```

# Save Data files In RData
```{r}
# save(Data_Pclass1,file = "data_Pclass1.RData")
# save(Data_Pclass2,file = "data_Pclass2.RData")
# save(Data_Pclass3,file = "data_Pclass3.RData")
# save(Data_Pclass4,file = "data_Pclass4.RData")
# save(Data_Pclass5,file = "data_Pclass5.RData")
# save(Data_Pclass6,file = "data_Pclass6.RData")
# save(Data_Pclass7,file = "data_Pclass7.RData")
```

# Save Data files In RData
```{r}

Data_Pclass1 <- subset(Data_Pclass1, select = -c(price_usd_normalized) )
write.csv(Data_Pclass1,file = "../../../Data/datacsv_Pclass1.csv")
Data_Pclass2 <- subset(Data_Pclass2, select = -c(price_usd_normalized) )
write.csv(Data_Pclass2,file = "../../../Data/datacsv_Pclass2.csv")
Data_Pclass3 <- subset(Data_Pclass3, select = -c(price_usd_normalized) )
write.csv(Data_Pclass3,file = "../../../Data/datacsv_Pclass3.csv")
Data_Pclass4 <- subset(Data_Pclass4, select = -c(price_usd_normalized) )
write.csv(Data_Pclass4,file = "../../../Data/datacsv_Pclass4.csv")
Data_Pclass5 <- subset(Data_Pclass5, select = -c(price_usd_normalized) )
write.csv(Data_Pclass5,file = "../../../Data/datacsv_Pclass5.csv")
Data_Pclass6 <- subset(Data_Pclass6, select = -c(price_usd_normalized) )
write.csv(Data_Pclass6,file = "../../../Data/datacsv_Pclass6.csv")
```





#removing all columns with NA 
```{r}

df <- Data_Pclass1
# df$consumer < - as.factor(df$consumer)

# df <- df[ , colSums(is.na(df)) == 0]
#An alternative way is to use apply:
# df <- df[ , apply(df, 2, function(x) !any(is.na(x)))]
```
# changing name for 
```{r}
colnames(df)[which(names(df) == "price_usd_normalized.prices_normalized")] <- "price_usd_normalized"

names(df)
```
#all data converted to facotr
```{r}
# df <- as.factor(df)
```


#Boruta
Limitations
Some limitations of the Boruta package are worth highlighting:

It only works with classification (factor) target variables. I am not sure why: as far as I remember, the random forest algorithm also provides a variable significance score when it is used as a predictor, not just when it is run as a classifier.
It does not handle missing (NA) values at all. This is quite a problem when working with real data sets, and a shame as random forests are in principle very good at handling missing values. A simple re-write of the package using the party package instead of randomForest should be able to fix this issue.
It does not seem to be completely stable. I have crashed it on several real-world data sets and am working on a minimal set to send to the authors.


```{r}
library(Boruta)

# sample_data <- df[sample(nrow(df), 10000), ]
# df <- as.factor(df)
b <- Boruta(score ~ 
                                  srch_id + 
                                  site_id +                     
                                  prop_id + 
                                  prop_starrating + 
                                  prop_review_score + 
                                  prop_brand_bool + 
                                  prop_location_score1 + 
                                  prop_location_score2 + 
                                  position + 
                                  price_usd +
                                  promotion_flag + 
                                  srch_saturday_night_bool +
                                  random_bool+ 
                                  click_bool +
                                  booking_bool+             
                                  price_usd_normalized+
                                  consumer+
                                  Pclass
                  ,data=df, doTrace = 0)



print(b)
```

Boruta performed 99 iterations in 6.879991 mins.
 13 attributes confirmed important: date_time, prop_brand_bool, prop_country_id, prop_location_score1,
prop_location_score2 and 8 more;
 5 attributes confirmed unimportant: prop_id, srch_children_count, srch_room_count, srch_saturday_night_bool,
visitor_hist_starrating;
 5 tentative attributes left: consumer, position, promotion_flag, srch_adults_count, srch_id;



#random forest
```{r}

library(caret)
library(randomForest)
library(doParallel)

cores <- 4
cl <- makePSOCKcluster(cores)
registerDoParallel(cl)


# 3 times cross validation.
my_control <- trainControl(method = "cv", number = 3 )

my_forest <- train(score ~ 
                                  # srch_id + 
                                  # site_id +                     
                                  # prop_id + 
                                  prop_starrating +
                                  prop_review_score +
                                  prop_brand_bool +
                                  prop_location_score1 +
                                  prop_location_score2 +
                                  position +
                                  price_usd +
                                  promotion_flag +
                                  # srch_saturday_night_bool +
                                  # random_bool+ 
                                  # click_bool +
                                  # booking_bool+
                                  # consumer+
                                  Pclass ,
                   data = df,
                   method = "parRF",
                   ntree = 250,
                   trControl=my_control)


summary(my_forest)
# library(randomForest)
# fit_randomForest_1 <- randomForest(score ~ 
#                                   # srch_id + 
#                                   # site_id +                     
#                                   # prop_id + 
#                                   prop_starrating +
#                                   prop_review_score +
#                                   prop_brand_bool +
#                                   prop_location_score1 +
#                                   prop_location_score2 +
#                                   position +
#                                   price_usd +
#                                   promotion_flag +
#                                   # srch_saturday_night_bool +
#                                   # random_bool+ 
#                                   # click_bool +
#                                   # booking_bool+
#                                   # consumer+
#                                   Pclass 
#                       ,
#                       data=df, 
#                       importance=TRUE, 
#                       ntree=2)
# 
# 
# summary(fit_randomForest_1)


```







```{r}
# install.packages('party')
library(party)
 set.seed(415)
fit_cforest <- cforest(score ~ 
                                  # srch_id + 
                                  # site_id +                     
                                  # prop_id + 
                                  prop_starrating +
                                  prop_review_score +
                                  prop_brand_bool +
                                  prop_location_score1 +
                                  prop_location_score2 +
                                  position +
                                  price_usd +
                                  promotion_flag +
                                  # srch_saturday_night_bool +
                                  # random_bool+ 
                                  # click_bool +
                                  # booking_bool+
                                  # consumer+
                                  Pclass 
                                  ,
                 data = df, 
                 controls=cforest_unbiased(ntree=20, mtry=3))

```




K-means
```{r}
# df <- na.omit(df)
# df <- df[!is.na(df[,1]),]
set.seed(20)
# df<- df[-c("price_usd_normalized")]
library(fpc)

clusters <- pamk(df[29:30], krange=2:10, criterion="ch", usepam=FALSE, diss=FALSE)
# cluster <- kmeans(df[29:30], 200)
# cluster
```

```{r}
# Model Based Clustering
citation("mclust")
library(mclust)
fit <- Mclust(df[1:20])
plot(fit) # plot results 
summary(fit) # display the best model
```


```{r}
install.packages("data.table")
library(data.table)
install.packages("fastmatch")
library("fastmatch")
install.packages("microbenchmark")
library('microbenchmark')
```

```{r}

# DData <- read.csv("../../../Data/data.csv", header= TRUE)
DData <- fread(file = "../../../Data/data.csv", select = c("srch_id","click_bool","booking_bool","prop_id"))
```

```{r}
# predictions <- fread("../../../Data/predictions_KNeighborsClassifier.csv", header= TRUE)
# predictions <- fread("../../../Data/predictions_RandomForestClassifier.csv", header= TRUE)
predictions <- fread("../../../Data/predictions_DecisionTreeClassifier.csv", header= TRUE)
```


```{r}
ranked = data.frame(predictions$srch_id,predictions$prop_id,predictions$score)

names(ranked)[1] <- "srch_id"
names(ranked)[2] <- "prop_id"
names(ranked)[3] <- "score"
```



# calculation prof [he just explained a simple version]
```{r}
# Subset Data
srch_idP <- unique(ranked[,1])
out <- subset(DData, srch_id %in% srch_idP)

# Calculate basic score 
out$scored <- out[,2] +4* out[,3]

# Set up Position
out$position <- ave(out$srch_id, out$srch_id, FUN = seq_along)

# Calculate discounted score
out$Dscore <- out$scored / (out$position)

# Delete variables
out$click_bool <- NULL
out$booking_bool <- NULL

# Calculate discounted score
out$Dscore <- (2^out$score - 1)/ log2(out$position + 1)
sums <- aggregate(out$Dscore, by=list(out$srch_id), FUN= sum)  # Sum each score for each group-id

# Calculate max score possible
out_max <- out[order(out$srch_id, -out$scored),]
out_max$position <- ave(out_max$srch_id, out_max$srch_id, FUN = seq_along)
out_max$Dscore <-  (2^out_max$score - 1)/ log2(out_max$position + 1)
sums_max <- aggregate(out_max$Dscore, by=list(out_max$srch_id), FUN= sum)  # Sum each score for each group-id

# Calculate NDCG
a<- sums/ sums_max
NDCG <- sum(a[,2])/nrow(sums)
NDCG
```
Random forest nDCG 0.3494453
K-Neighbors nDCG 0.3494571
Decision Tree 0.3494571













# Calculation /log2
```{r}
# Subset Data
srch_idP <- unique(ranked[,1])
srch_DD <- unique(DData[,1])

out1<- ranked
out2 <- subset(DData,  DData$srch_id %in% srch_idP)

out <- merge(out1,out2 , by=c('srch_id','prop_id'))
out<-out[order(out[,1], -out[,3]),]


# Calculate basic score 
out$scored <- out[,4] + 4* out[,5]
out$click_bool <- NULL
out$booking_bool <- NULL

# Set up Position
out$position <- ave(out$srch_id, out$srch_id, FUN = seq_along)

# Calculate discounted score
out$Dscore <- (2^out$score - 1)/ log2(out$position + 1)
sums <- aggregate(out$Dscore, by=list(out$srch_id), FUN= sum)  # Sum each score for each group-id

# Calculate max score possible
out_max <- out[order(out$srch_id, -out$scored),]
out_max$position <- ave(out_max$srch_id, out_max$srch_id, FUN = seq_along)
out_max$Dscore <-  (2^out_max$score - 1)/ log2(out_max$position + 1)
sums_max <- aggregate(out_max$Dscore, by=list(out_max$srch_id), FUN= sum)  # Sum each score for each group-id

# Calculate NDCG
a<- sums/ sums_max
a<- a[2:nrow(a),]
NDCG <- sum(a[,2])/nrow(sums)
NDCG
```

