
---
title: "Assignment 2 short"
output: html_notebook
---


```{r}
# Data loading
rm(list=ls())
rm(list = ls())
```
# Load libraries
```{r}
library("ggplot2")
# install.packages("nortest")
library(nortest)
#install.packages("mvoutlier")
library(mvoutlier)
#install.packages("doBy")
library(doBy)
  # install.packages("anytime")
library(anytime)
  # install.packages("rpart")
library("rpart")
```
# Load rawdata set
```{r}
WD <- setwd("C:\\Users\\Piet\\Test\\Data-Mining\\assignment-2\\assignment2")
load("rawdata_environment.RData")
```
# Split data into normal data and competitor data
```{r}
columns <- c(28:51)
data <- subset(rawdata, select = -columns )
data_comp <- subset(rawdata, select = columns)
str(data)
```
# Split data into class: factors and integers
```{r}
columns <- c(2,5,6,10,12:14,16,25,26,29)
data.integers  <- subset(data, select = -columns )
data.factors   <- subset(data, select = columns)
data.factors_totransform <-subset(data.factors, select = c(3,6:11))         # Delete variable srch_id
datetime <- subset(data, select = c(2))
```
# Transform specific factors into numerics
```{r}
for (i in 1:7){
    data.factors_totransform[,i] <- as.numeric(as.character(data.factors_totransform[ ,i]))
}
for (i in 1:8){
data_comp[ , 3*i] <- as.numeric(as.character(data_comp[ ,3*i]))
}
table(is.na(data.factors_totransform$visitor_hist_adr_usd))
```



# Transform Date time
```{r}
data$date_time <-  anytime(as.factor(data$date_time))
data$year <- as.numeric(format(data$date_time,'%Y'))
data$month <- as.numeric(format(data$date_time,'%m'))
data$date_time <- data$year + (data$month / 12)
# 
```

# Put in transformed factors back
```{r}
data[ , c(6,13,14,16,25,26,29)] <- data.factors_totransform[ ,1:7]
```

# Delete unnecessary columns or values
```{r}
data$year <- NULL
data$month <- NULL
rm(columns, rawdata, datetime, data.factors_totransform)
```


# Missing values ----------------------------------------------------------------------------------------------------------------

```{r}
##############################
# Replacing missing observations of the variable prop_location_score2 by the mean
##############################
data$prop_location_score2[is.na(data$prop_location_score2)]<-mean(data$prop_location_score2[(!is.na(data$prop_location_score2))])
##############################
# Replace missing values of prop review score with the lowest rating value i.e. 1
##############################
data$prop_review_score[is.na(data$prop_review_score)] <- 1
##############################
# ANOVA regression classification for the prop_starrating
##############################
ANOVA_Sample<-cbind(data$prop_review_score,data$price_usd,data$prop_starrating)
ANOVA_Sample<-data.frame(ANOVA_Sample)
colnames(ANOVA_Sample)<-c("prop_review_score","price_usd","prop_starrating")
starFIT <- rpart(prop_starrating ~ prop_review_score+price_usd,data = ANOVA_Sample[ANOVA_Sample$prop_starrating!=0,], method = "anova")

ANOVA_Sample$prop_starrating[ANOVA_Sample$prop_starrating==0] <- round(predict(starFIT,data=data.frame(ANOVA_Sample[ANOVA_Sample$prop_starrating==0,],)))
#replace ald starrating varaible with the new predicted one
data$prop_starrating<-ANOVA_Sample$prop_starrating
           
```
# Remove unnecessary data
```{r}
rm(ANOVA_Sample, i, starFIT)
```

# Handling Outliers --------------------------------------------------------------------------------------------------------------------

# Replace prices above 10000 into the median price
```{r}
median(data$price_usd)
data$price_usd[data$price_usd>5000] <- median(data$price_usd)
data$price_usd[data$price_usd>2000] <- 2000


# https://stats.stackexchange.com/questions/70801/how-to-normalize-data-to-0-1-range
# normalize prices
prices_max <- aggregate(price_usd ~ srch_id, data = data, max)
prices_min <- aggregate(price_usd ~ srch_id, data = data, min)

data2 = merge(data,prices_max,by.x=1,by.y=1)
data2 = merge(data2,prices_min,by.x=1,by.y=1)

prices_normalized <- (data2$price_usd.x -data2$price_usd)/(data2$price_usd.y - data2$price_usd)

d <- data.frame(prices_normalized)
data$price_usd_normalized <- d
```

# place Outliers for percentage price difference with competitors
```{r}
a <- data_comp[ ,c(3,6,9,12,15,18,21,24)]
a[a > 300] <- 300
data_comp[ , c(3,6,9,12,15,18,21,24)] <- a

rm(a,d,prices_max,prices_min,prices_normalized,data2)
```
# Create New variables  -----------------------------------------------------------------------------------------------------------

# Creating Consumers class
```{r}
data$consumer <- "other"
data$consumer[data$srch_adults_count == 1] <- "single"
data$consumer[data$srch_adults_count == 2] <- "couple"
data$consumer[data$srch_children_count == 2] <- "Parents"
```

# Creating Socio Economic class [BIG LOOP]
```{r}
Means <- aggregate(price_usd ~ srch_id, data = data, mean)
Means[ ,2] <- findInterval(Means[,2], c(0,50, 100,150,225,500,1000,10000))

d <- data.frame(data[ ,c(1)])
names(d) <- c("srch_id")
a<- merge(d, Means, by="srch_id")
data$Pclass <- a[,2]

rm(a,d,Means)
```
# Creating Score variable 
```{r}
# If clicked, score is +1# If booked score is +5
data$score <- (data$click + 5* data$book)* data$position

hotelscores <- aggregate(score ~ prop_id, data = data, sum)
hotelclicks <- aggregate(click_bool ~ prop_id, data=data, sum)
hotelbooks <- aggregate(booking_bool ~ prop_id, data=data, sum)

hist(log(hotelclicks[,2]), prob = TRUE)
curve(dexp(x, rate = 2.5), col = 2, lty = 2, lwd = 2, add = TRUE)

hist(log(hotelbooks[,2]), prob = TRUE)
curve(dexp(x, rate = 2.5), col = 2, lty = 2, lwd = 2, add = TRUE)
```

# remove al unnecessary data
```{r}
rm(hotelbooks, hotelclicks,hotelscores,booked_prices)
```

# Create small data set
```{r}
smalldataset <- data[,c(1,9:17,26:28,30:34)]
```

# Split Data into Consumer types:
```{r}
Data_c<-split(data, data$consumer)

Data_consumer1 <- as.data.frame(Data_c[1])
Data_consumer2 <- as.data.frame(Data_c[2])
Data_consumer3 <- as.data.frame(Data_c[3])
Data_consumer4 <- as.data.frame(Data_c[4])

names(Data_consumer1) <- names(Data_consumer2) <-names(Data_consumer3) <-names(Data_consumer4) <- c("srch_id","date_time","site_id","visitor_location_country_id","visitor_hist_starrating","visitor_hist_adr_usd","prop_country_id","prop_id","prop_starrating","prop_review_score","prop_brand_bool","prop_location_score1","prop_location_score2",
"prop_log_historical_price","position","price_usd","promotion_flag","srch_destination_id","srch_length_of_stay","srch_booking_window",
"srch_adults_count","srch_children_count","srch_room_count","srch_saturday_night_bool","srch_query_affinity_score","orig_destination_distance","random_bool","click_bool","gross_bookings_usd","booking_bool","price_usd_normalized.prices_normalized","consumer","Pclass","score")
```

# Split Data into Socio-Economic Data frames

```{r}
Data_p<-split(data, data$Pclass)

Data_Pclass1 <- as.data.frame(Data_p[1])
Data_Pclass2 <- as.data.frame(Data_p[2])
Data_Pclass3 <- as.data.frame(Data_p[3])
Data_Pclass4 <- as.data.frame(Data_p[4])
Data_Pclass5 <- as.data.frame(Data_p[5])
Data_Pclass6 <- as.data.frame(Data_p[6])
Data_Pclass7 <- as.data.frame(Data_p[7])


names(Data_Pclass1 ) <- names(Data_Pclass2) <-names(Data_Pclass3) <-names(Data_Pclass4) <- names(Data_Pclass5) <-names(Data_Pclass6) <-names(Data_Pclass7) <- c("srch_id","date_time","site_id","visitor_location_country_id","visitor_hist_starrating","visitor_hist_adr_usd","prop_country_id","prop_id","prop_starrating","prop_review_score","prop_brand_bool","prop_location_score1","prop_location_score2",
"prop_log_historical_price","position","price_usd","promotion_flag","srch_destination_id","srch_length_of_stay","srch_booking_window",
"srch_adults_count","srch_children_count","srch_room_count","srch_saturday_night_bool","srch_query_affinity_score","orig_destination_distance","random_bool","click_bool","gross_bookings_usd","booking_bool","price_usd_normalized.prices_normalized","consumer","Pclass","score")







```
# Split Consumer Data into Socio-Economic class [28 DATASETS]
```{r}
# Data_consumer1_Pclass <- split(Data_consumer1, Data_consumer1[,33])
# Data_consumer1_Pclass1 <- as.data.frame(Data_consumer1_Pclass[1])
# Data_consumer1_Pclass2 <- as.data.frame(Data_consumer1_Pclass[2])
# Data_consumer1_Pclass3 <- as.data.frame(Data_consumer1_Pclass[3])
# Data_consumer1_Pclass4 <- as.data.frame(Data_consumer1_Pclass[4])
# Data_consumer1_Pclass5 <- as.data.frame(Data_consumer1_Pclass[5])
# Data_consumer1_Pclass6 <- as.data.frame(Data_consumer1_Pclass[6])
# 
# Data_consumer2_Pclass <- split(Data_consumer2, Data_consumer2[,33])
# Data_consumer2_Pclass1 <- as.data.frame(Data_consumer2_Pclass[1])
# Data_consumer2_Pclass2 <- as.data.frame(Data_consumer2_Pclass[2])
# Data_consumer2_Pclass3 <- as.data.frame(Data_consumer2_Pclass[3])
# Data_consumer2_Pclass4 <- as.data.frame(Data_consumer2_Pclass[4])
# Data_consumer2_Pclass5 <- as.data.frame(Data_consumer2_Pclass[5])
# Data_consumer2_Pclass6 <- as.data.frame(Data_consumer2_Pclass[6])
# 
# Data_consumer3_Pclass <- split(Data_consumer3, Data_consumer3[,33])
# Data_consumer3_Pclass1 <- as.data.frame(Data_consumer3_Pclass[1])
# Data_consumer3_Pclass2 <- as.data.frame(Data_consumer3_Pclass[2])
# Data_consumer3_Pclass3 <- as.data.frame(Data_consumer3_Pclass[3])
# Data_consumer3_Pclass4 <- as.data.frame(Data_consumer3_Pclass[4])
# Data_consumer3_Pclass5 <- as.data.frame(Data_consumer3_Pclass[5])
# Data_consumer3_Pclass6 <- as.data.frame(Data_consumer3_Pclass[6])
# 
# Data_consumer4_Pclass <- split(Data_consumer4, Data_consumer4[,33])
# Data_consumer4_Pclass1 <- as.data.frame(Data_consumer4_Pclass[4])
# Data_consumer4_Pclass2 <- as.data.frame(Data_consumer4_Pclass[2])
# Data_consumer4_Pclass3 <- as.data.frame(Data_consumer4_Pclass[3])
# Data_consumer4_Pclass4 <- as.data.frame(Data_consumer4_Pclass[4])
# Data_consumer4_Pclass5 <- as.data.frame(Data_consumer4_Pclass[5])
# Data_consumer4_Pclass6 <- as.data.frame(Data_consumer4_Pclass[6])
```


# Save Data files
```{r}
save(Data_Pclass1,file = "data_Pclass1.RData")
save(Data_Pclass2,file = "data_Pclass2.RData")
save(Data_Pclass3,file = "data_Pclass3.RData")
save(Data_Pclass4,file = "data_Pclass4.RData")
save(Data_Pclass5,file = "data_Pclass5.RData")
save(Data_Pclass6,file = "data_Pclass6.RData")
save(Data_Pclass7,file = "data_Pclass7.RData")
```




















